---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# transcats

<!-- badges: start -->
`r lifecycle::badge('experimental')`
<!-- badges: end -->

The goal of transcats is to translate the variable names and titles and values of dataframes 
containing containing categorical and other data. These translations are
made using editable translation tables to allow users to edit and verify
translations.

## Installation

You can install the development version of transcats from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CarwilB/transcats")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(transcats)
## basic example code
names(forcats::gss_cat)
set_title_lang("es")
set_var_name_table(gss_var_table)
variable_names_vector(forcats::gss_cat)
```

## Translating tabular data

There's a longer workflow for translating categorical data (see the vignette "A workflow for creating translation tables"), but the net result is full translation of categorical data.

```{r gss-before-and-after, echo = FALSE}
knitr::kable(head(forcats::gss_cat, 8))

gss_cat_fr <- readRDS("inst/extdata/gss_cat_fr.RDS")
knitr::kable(head(gss_cat_fr, 8))
```


